---
title: "Quick Analysis Example"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: paper
    navbar:
      - {icon: "ion-social-github", href: "https://github.com/AdeelK93/QuickAnalysis", align: right}
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(Cairo)
options(shiny.usecairo=T)
library(dygraphs)
library(rhandsontable)
suppressMessages(library(DT))
source('QuickAnalysis.R')
```

Import {data-orientation=columns}
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

An example for importing data and making plots  
  
```{r Sidebar}
options(shiny.maxRequestSize=30*1024^2) #30 mb limit
fileInput(
  'fileschosen',
  'Accepted formats: csv, xls, xlsx (any combination)',
  multiple = T,
  accept = c('.csv', '.xls', '.xlsx')
  )
imported.orig <- reactive({
  validate(need(!is.null(input$fileschosen),F))
  x <- tryCatch(import(input$fileschosen),error=function(e) NULL)
  validate(need(x,"add more descriptive error messages here"))
  x
})
```

* For excel files with multiple sheets, only sheets with the max number of columns will be imported
* Data must have column names present in order to be successfully imported   
* You can download the merged dataset as a zipped csv below:

```{r Download}
output$download <- downloadHandler(paste('data-', Sys.Date(), '.zip', sep=''),
   content = function(file) if(!is.null(imported())) {
     setwd(tempdir())
     names <- paste0(levels(as.factor(imported()$Battery.ID)),".csv")
     #split up the data by ID and reduce file size
     spl <- lapply(split(imported(),imported()$Battery.ID),
                   function(x) select(x,-Battery.ID,-Type,-Filename,
                                      -TimeHr,-TimeMin,-StepTimeHr,-StepTimeMin))
     mapply(write_csv,spl,names)
     #the warning is to deal with windows computers
     tryCatch(zip(zipfile=file, files=names),warning=function(e) zip(zipfile=file, files=names,
              zip = "C:/Program Files/Rtools/bin/zip"))
   },
   contentType = "application/zip"
)
fluidPage(downloadButton('download', 'Download csv'))
```

Column {data-width=400 .tabset .tabset-fade}
-------------------------------------

###Choose variables
```{r vars.input}
#remove text columns
graphnames.orig <- reactive(colnames(imported.orig()[sapply(imported.orig(), is.numeric)]))
output$voltage <- renderUI({ 
  selectInput("voltage","Voltage:",graphnames.orig(),
            agrep.best("Voltage",colnames(imported.orig())),T)
})
voltage.sorted <- reactive(if(!is.null(imported.orig())) {
  #rowMeans=merging columns in a moderately efficient way
  #rowSums can't handle 0s well
  rowMeans(imported.orig()[input$voltage],na.rm=T)
})
output$current <- renderUI({ 
  selectInput("current","Current:",graphnames.orig(),
            agrep.best("Current",colnames(imported.orig())),T)
})
current.sorted <- reactive(if(!is.null(imported.orig())) {
  rowMeans(imported.orig()[input$current],na.rm=T)
})
output$amphours <- renderUI({ 
  selectInput("amphours","Capacity (Amp-hours):",graphnames.orig(),
            agrep.best("Amp.Hours",colnames(imported.orig())),T)
})
amphours.sorted <- reactive(if(!is.null(imported.orig())) {
  rowMeans(imported.orig()[input$amphours],na.rm=T)
})
output$totaltime <- renderUI({ 
  selectInput("totaltime","Total elapsed time:",graphnames.orig(),
            agrep.best("Total.Time",colnames(imported.orig())),T)
})
totaltime.sorted <- reactive(if(!is.null(imported.orig())) {
  x <- rowMeans(imported.orig()[input$totaltime],na.rm=T)
  if(min(x[x>0],na.rm=T)<0.05) { #time in days?
    x <- ave(x,imported.orig()$Filename,FUN=function(x) {
      #only modify files with time reporting in days
      if(min(x[x>0],na.rm=T)<0.01) x*24*3600
      else x
    })
  }
  if(sum(is.na(x))) return(x)
  #verify that data is monotonic
  x <- ave(x,imported.orig()$Filename,FUN=function(y) {
      if(!all(y==cummax(y))) y <- as.monotonic(y) #nonmonotonic
      else y
    })
  x
})
output$steptime <- renderUI({ 
  selectInput("steptime","Step time:",graphnames.orig(),
            agrep.best("Step.Time",colnames(imported.orig())),T)
})
steptime.sorted <- reactive(if(!is.null(imported.orig())) {
  x <- rowMeans(imported.orig()[input$steptime],na.rm=T)
  if(min(x[x>0],na.rm=T)<0.05) { #time in days?
    x <- ave(x,imported.orig()$Filename,FUN=function(x) {
      #only modify files with time reporting in days
      if(min(x[x>0],na.rm=T)<0.01) x*24*3600
      else x
    })
  }
  x
})
output$step <- renderUI({ 
  selectInput("step","Step index:",graphnames.orig(),
            agrep.best("Step",colnames(imported.orig())),T)
})
step.sorted <- reactive(if(!is.null(imported.orig())) {
  rowMeans(imported.orig()[input$step],na.rm=T)
})
output$cycle <- renderUI({ 
  selectInput("cycle","Cycle counter:",graphnames.orig(),
            agrep.best("Cycle",colnames(imported.orig())),T)
})
cycle.sorted <- reactive(if(!is.null(imported.orig())) {
  x <- rowMeans(imported.orig()[input$cycle],na.rm=T)
  if(sum(is.na(x))) return(x)
  #verify that data is monotonic
  x <- ave(x,imported.orig()$Filename,FUN=function(y) {
      if(!all(y==cummax(y))) y <- as.monotonic(y) #nonmonotonic
      else y
    })
  x
})

incomplete <- reactive({if(is.null(imported())) return(NULL)
  #count the number of missing values, for heatmap and diagnostics
  sum(sapply(imported()[c("Battery.ID",stdnames)], function(x) sum(is.na(x))))
  })
```

```{r import.vars}
fluidPage(column(12,div(
  style = "height:70px;",
  htmlOutput("voltage"),
  htmlOutput("current"),
  htmlOutput("amphours"),
  htmlOutput("totaltime"),
  htmlOutput("steptime"),
  htmlOutput("step"),
  htmlOutput("cycle"),
  renderText(if(!is.null(imported())) paste("If your dataset has different column names between files, you must select all applicable columns above.",incomplete(),
              "missing values found, see heatmap for more details."))
)))

imported.sorted <- reactive({
  if(is.null(imported.orig())) return(NULL)
  x <- imported.orig()[setdiff(colnames(imported.orig()),c(
    input$voltage,input$current,input$amphours,input$totaltime,
    input$steptime,input$step,input$cycle))] #drop columns
  x <- data.frame(Voltage=voltage.sorted(),Current=current.sorted(),
                  Amp.Hours=amphours.sorted(),Total.Time=totaltime.sorted(),
                  Step.Time=steptime.sorted(),Step=step.sorted(),
                  Cycle=cycle.sorted(),x)
  x <- mutate(x, #add time data
    TimeMin=Total.Time/60, TimeHr=Total.Time/3600,
    StepTimeMin=Step.Time/60, StepTimeHr=Step.Time/3600
    )
  tryCatch(calculaterechargefactor(x),error=function(e) x)
})
imported <- reactive({ #this is the final sorted dataset to be used by analytical functions
  if(is.null(imported.sorted())) return(NULL)
  x <- select(imported.sorted(), -Type, -Battery.ID)
  suppressMessages(left_join(x,labs())) %>%
    arrange(Type,Battery.ID) %>%
    seg.stitch() %>%
    mutate(Type=as.factor(Type),Battery.ID=as.factor(Battery.ID)) %>%
    filter(Type!="skip")
})
```

###Heatmap
Heatmap shows where missing values are concentrated (if applicable)
```{r heatmap}
output$heatmap <- renderPlotly(if(!is.null(imported())){
  tryCatch(ggplotly({
    heat <- aggregate(imported()[stdnames],list(imported()$Battery.ID),function(x) sum(is.na(x)))
    heat <- suppressMessages(melt(heat))
    colnames(heat) <- c("Battery.ID","Column","Missing.Values")
    ggplot(heat,aes(Column,Battery.ID,fill=Missing.Values)) + 
      geom_tile()+scale_fill_continuous(low="gray95",high="firebrick") + 
      theme_minimal() + theme(axis.text.x = element_text(angle = 30,
        hjust = 1),legend.position="none")+ylab(" ")+xlab(" ")
  }) %>% config(displayModeBar = F),error=function(e) ggplotly(ggplot()))
})
plotlyOutput("heatmap")
#renderText(if(identical(incomplete(),0)) return("No missing values remain! All data has been accounted for."))
```

###Diagnostic
```{r diagnostic}
radioButtons("diag.choice",NULL,c("Summary","Structure","Head","Tail"),inline=T)
renderPrint(switch(input$diag.choice,
                   "Summary"=summary(imported()),
                   "Structure"=str(imported()),
                   "Head"=head(imported()),
                   "Tail"=tail(imported())
))
```

Column {data-width=600}
-------------------------------------

###Label Table
Will ignore files with type "skip".
```{r labeltable}
values <- reactiveValues(labels=NULL)
observeEvent(imported.orig(), {
  values$labels <- data.frame(Filename=imported.orig()$Filename,
                              Type=as.character(imported.orig()$Type),
                              Battery.ID=as.character(imported.orig()$Battery.ID),
                              stringsAsFactors=F)[!duplicated(imported.orig()$Filename),]
})
output$labels.hot <- renderRHandsontable(if(!is.null(values$labels)){
  rhandsontable(values$labels, contextMenu=F, maxRows=length(unique(imported.orig()$Filename)),
                rowHeaders = NULL, stretchH = "all") %>%
    hot_col("Filename", readOnly = T)
})
rHandsontableOutput("labels.hot")
labs <- reactive({
  if(!is.null(input$labels.hot)) hot_to_r(input$labels.hot)
  else values$labels
})
```

###Customize Colors
Hex colors or any of [these named colors](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf).
```{r colortable}
values <- reactiveValues(colors=NULL)
observeEvent(labs(), {
  values$colors <- data.frame(Type=sort(unique(labs()$Type[labs()$Type!="skip"])),
    Color=rainbow_hcl(length(unique(labs()$Type[labs()$Type!="skip"])),70),
    stringsAsFactors=F)
})
observeEvent(imported.orig(), {
  values$colors <- data.frame(Type=sort(unique(labs()$Type[labs()$Type!="skip"])),
    Color=rainbow_hcl(length(unique(labs()$Type[labs()$Type!="skip"])),70),
    stringsAsFactors=F)
})
output$colors.hot <- renderRHandsontable(if(!is.null(values$colors)){
  rhandsontable(values$colors, contextMenu=F,
                maxRows=length(unique(labs()$Type[labs()$Type!="skip"])),
                rowHeaders = NULL) %>%
    hot_col("Type", readOnly = T)
})
rHandsontableOutput("colors.hot")
cols <- reactive({ #this is the color data, by type
  if(!is.null(input$colors.hot)) hot_to_r(input$colors.hot)
  else values$colors
})
cols.cast <- reactive({ #this is the color data, by ID
  if(!is.null(cols())){
    x <- suppressMessages(arrange(left_join(filter(labs(),Type!="skip"),
                                       cols()),Battery.ID))
    x$Battery.ID <- gsub(" ?#[[:digit:]]+$","",x$Battery.ID)
    x
  }
})
```

Explore {data-orientation=columns data-navmenu="Continuous"}
=====================================

Column {data-width=200 .tabset .tabset-fade}
-------------------------------------

### Choose options
Select continuous variables for graphing  
  
```{r xy.options}
graphnames <- reactive(if(!is.null(imported())) colnames(imported()[sapply(imported(),
                                                                                is.numeric)]))
timeunits <- reactive(if(!is.null(imported.sorted())) {
  x <- max(imported.sorted()$Total.Time, na.rm = T)
  if(x<300) return("Total.Time") #under 5 minutes -> seconds
  else if(x<7200) return("TimeMin") #under 2 hours -> minutes
  else return("TimeHr") #hours
})

#this data is fed into the continuous variable graph
imported.xy <- reactive(if(!is.null(imported())) {
  if(is.null(input$xy.cycle)) return(imported())
  else if(input$xy.cycle==0) x <- imported()
  else { #baseline time stamp correction
    x <- imported()[imported()$Cycle==input$xy.cycle,] %>%
    within({Total.Time <- ave(Total.Time, Battery.ID, FUN=function(x) x-min(x))}) %>%
    mutate(TimeHr=Total.Time/3600,TimeMin=Total.Time/60)
  }
  if(input$xy.step) x <- filter(x,Step==input$xy.step)
  x <- tryCatch(filter(x,
         Voltage>=input$xy.voltage[1],Voltage<=input$xy.voltage[2],
         Current>=input$xy.current[1],Current<=input$xy.current[2],
         Amp.Hours>=input$xy.amphours[1],Amp.Hours<=input$xy.amphours[2],
         Total.Time>=input$xy.totaltime[1],Total.Time<=input$xy.totaltime[2],
         Step.Time>=input$xy.steptime[1],Step.Time<=input$xy.steptime[2]
         ),error=function(e) x)
  if(input$xy.avg & !is.null(x)) {
    x <- avgsem(select_(x,input$top.yn,input$bottom.yn,input$bottom.xn,
                        "Type","Battery.ID"),input$bottom.xn)
  }
  return(x)
})

#remove filtered out colors
xy.cols <- reactive(if(!is.null(imported.xy())) {
  cols()$Color[cols()$Type %in% imported.xy()$Type]
})
xy.cols.cast <- reactive(if(!is.null(imported.xy())) {
  cols.cast()$Color[cols.cast()$Battery.ID %in% imported.xy()$Battery.ID]
})

output$top.yn <- renderUI({ 
selectInput("top.yn","Top y-axis:",graphnames(),"Current")
  })
output$bottom.yn <- renderUI({ 
selectInput("bottom.yn","Bottom y-axis:",graphnames(),"Voltage")
  })
output$bottom.xn <- renderUI({ 
selectInput("bottom.xn","Common x-axis:",graphnames(),timeunits())
  })

fluidPage(column(12,div(
  style = "height:80px;",
  htmlOutput("top.yn"),
  htmlOutput("bottom.yn"),
  htmlOutput("bottom.xn"),
  checkboxInput("xy.avg","Average/SEM by type"),
  textOutput("legendDivID")
)))
```

###Filter
```{r xy.filter}
#filter dataset for continuous variable analysis
#filter min/max determine the bounds of the sliders
output$xy.voltage <- renderUI({ 
  sliderInput("xy.voltage","Select a voltage range:",filter.min()[1],filter.max()[1],
            c(filter.min()[1],filter.max()[1]),0.1)
  })
output$xy.current <- renderUI({ 
  sliderInput("xy.current","Select a current range:",filter.min()[2],filter.max()[2],
            c(filter.min()[2],filter.max()[2]),0.1)
  })
output$xy.amphours <- renderUI({ 
  sliderInput("xy.amphours","Select a capacity range:",filter.min()[3],filter.max()[3],
            c(filter.min()[3],filter.max()[3]),0.1)
  })
output$xy.totaltime <- renderUI({ 
  sliderInput("xy.totaltime","Select a total time range:",filter.min()[4],filter.max()[4],
            c(filter.min()[4],filter.max()[4]),1)
  })
output$xy.steptime <- renderUI({ 
  sliderInput("xy.steptime","Select a step time range:",filter.min()[5],filter.max()[5],
            c(filter.min()[5],filter.max()[5]),1)
  })
output$xy.step <- renderUI({ 
  sliderInput("xy.step","Is there a step to isolate? (0 for no)",0,
              tryCatch(max(imported.sorted()$Step),
                       error=function(e) 1),0,1,T)
})
output$xy.cycle <- renderUI({ 
  sliderInput("xy.cycle","Is there a cycle to isolate? (0 for no)",0,
              tryCatch(max(imported.sorted()$Cycle),
                       error=function(e) 1),0,1,T)
})

fluidPage(column(12,div(
  style = "height:80px;",
  htmlOutput("xy.voltage"),
  htmlOutput("xy.current"),
  htmlOutput("xy.amphours"),
  htmlOutput("xy.totaltime"),
  htmlOutput("xy.steptime"),
  htmlOutput("xy.step"),
  htmlOutput("xy.cycle")
)))
```

Column
-----------------------------------------------------------------------

### Top Graph {.no-title}
```{r top.graph}
renderDygraph(withProgress(
  message="Rendering plot...",
  dygraph.cast(imported.xy(),input$bottom.xn,input$top.yn,input$bottom.xn,
               input$top.yn,xy.cols.cast(),xy.cols(),group="brc")
))
```

### Bottom Graph {.no-title}
```{r bottom.graph}
renderDygraph(withProgress(
  message="Rendering plot...",
  dygraph.cast(imported.xy(),input$bottom.xn,input$bottom.yn,input$bottom.xn,
               input$bottom.yn,xy.cols.cast(),xy.cols(),group="brc")
))
```

Share {data-orientation=columns data-navmenu="Continuous"}
=====================================

Column {data-width=250 .tabset .tabset-fade}
-------------------------------------
    
### Choose options
Customize continuous variable chart for sharing:
```{r xypublish.options}
fluidPage(
  #checkboxInput("xypub.both","Include bottom graph (not yet working)"),
  selectInput("xypub.theme","Graph theme:",c("Default","Minimal","Grayscale")),
  selectInput("xypub.legend","Legend position:",c("None","Side"="right","Above"="top",
              "Below"="bottom","Top-left"="c(0,1)","Top-right"="c(1,1)",
              "Bottom-left"="c(0,0)","Bottom-right"="c(1,0)")),
  sliderInput("xypub.fsize","Font size:",10,20,12,0.5),
  textInput("xypub.title","Chart title:",""),
  helpText("Download chart options:"),
  splitLayout(
    numericInput("xypub.savew","Width:",12),
    numericInput("xypub.saveh","Height:",8),
    downloadButton("xypub.png","PNG"),
    downloadButton("xypub.svg","SVG")
  )
)
#linesize?
```

###Additional Options
Customize continuous variable chart for sharing:
```{r xypublish.options2}
fluidPage(
  helpText("X-axis options:"),
  textInput("xypub.xlab","X-axis label:",""),
  splitLayout(
    numericInput("xypub.x1","X start:",NA),
    numericInput("xypub.x2","X end:",NA)
  ),
  helpText("Y-axis options:"),
  textInput("xypub.ylab","Y-axis label:",""),
  splitLayout(
    numericInput("xypub.y1","Y start:",NA),
    numericInput("xypub.y2","Y end:",NA)
  ),
  #splitLayout(
  #  textInput("xypub.y1b","Y2 start:"),
  #  textInput("xypub.y2b","Y2 end:")
  #),
  helpText("Horizontal line options:"),
  splitLayout(
    textInput("xyhline.col","Color:","None"),
    numericInput("xyhline.val","Position:",0),
    numericInput("xyhline.size","Size:",0.8,step=.2)
  )
)
```

Column {data-width=700}
-------------------------------------

### Graph {.no-title}
```{r xypublish.graph}
xyline1 <- reactive(if(!is.null(imported.xy())) {
  gg <- linegraph(imported.xy(),input$bottom.xn,input$top.yn) #avg/sem
  if(input$xy.avg) gg <- gg + scale_color_manual(values=xy.cols(),name="") +
    scale_fill_manual(values=xy.cols(),name="")
  else gg <- gg + scale_color_manual(values=xy.cols.cast(),name="") #regular
  gg
})
renderPlot(withProgress(message="Rendering...",xypub.graph()))
xypub.graph <- reactive(if(!is.null(imported.xy())) {
  #these are the x-y limits
  xlim <- c(input$xypub.x1,input$xypub.x2)
  if(any(is.na(xlim))) xlim <- NULL
  ylim <- c(input$xypub.y1,input$xypub.y2)
  if(any(is.na(ylim))) ylim <- NULL
  
  gg <- xyline1() + coord_cartesian(xlim=xlim,ylim=ylim)
  #if(input$xypub.both){
  # gg2 <- xyline2()
  #}
  
  if(input$xyhline.col!="None" & input$xyhline.col!="none" & nchar(input$xyhline.col)){
    gg <- gg + geom_hline(aes_(yintercept=input$xyhline.val),linetype=2,
                          color=input$xyhline.col,size=input$xyhline.size)
  }
  if(input$xypub.theme=="Default") gg <- gg + theme_gray(base_size=input$xypub.fsize)
  if(input$xypub.theme=="Minimal") gg <- gg + theme_bw(base_size=input$xypub.fsize)
  if(input$xypub.theme=="Grayscale") gg <- gg + theme_pub(base_size=input$xypub.fsize) +
      scale_fill_grey(start=0,end=.9,name="") + scale_color_grey(start=0,end=.9,name="")
  
  if(!length(grep(",",input$xypub.legend))) gg <- gg + theme(legend.position=input$xypub.legend,
                                                           legend.title=element_blank())
  else gg <- gg + theme(legend.position=eval(parse(text=input$xypub.legend)),
                        legend.justification=eval(parse(text=input$xypub.legend)),
                        legend.title=element_blank())
  if(nchar(input$xypub.title)) gg <- gg + ggtitle(input$xypub.title)
  if(nchar(input$xypub.ylab)) gg <- gg + ylab(input$xypub.ylab)
  if(nchar(input$xypub.xlab)) gg <- gg + xlab(input$xypub.xlab)
  gg
})
output$xypub.png <- downloadHandler(paste('plot-', Sys.Date(), '.png', sep=''),
   content = function(file) if(!is.null(imported.xy())) {
     ggsave(file,device="png",width=input$xypub.savew,height=input$xypub.saveh)
   }
)
output$xypub.svg <- downloadHandler(paste('plot-', Sys.Date(), '.svg', sep=''),
   content = function(file) if(!is.null(imported.xy())) {
     ggsave(file,device="svg",width=input$xypub.savew,height=input$xypub.saveh)
   }
)
```

Explore {data-orientation=columns data-navmenu="Discrete"}
=====================================

Column {data-width=250 .tabset .tabset-fade}
-------------------------------------
    
### Choose options
Select discrete variables for graphing, eg: When Voltage is 6, what is Time?  
Use the 'filter' tab to further narrow down your dataset.  
  
```{r options}
output$varnames.yn <- renderUI({ 
  selectInput("options.yn","Name of the known variable:",graphnames())
  })
output$varnames.xn <- renderUI({ 
  selectInput("options.xn","Name of the unknown variable:",graphnames())
  })

fluidPage(
  htmlOutput("varnames.yn"),
  splitLayout(
    textInput("options.yv","Value of known variable:",
            placeholder="Numeric, or min/max"),
    numericInput("options.scalar","Scalar to multiply by:",1)
  ),
  
  htmlOutput("varnames.xn"),
  checkboxInput("avg","Average/SEM by type"),
  textInput("options.name","Name for this new variable:","Variable")
  
)
```
  
```{r calculating}
#this will calculatethe reduced dataset for discrete variable analysis
reduced <- reactive(if(!is.null(imported.filtered())){
  if(!nchar(input$options.yn) | !nchar(input$options.yv) | !nchar(input$options.xn) | !nchar(input$options.name)) return(NULL)
  options.data <- imported.filtered()
  options.name.orig <<- input$options.name
  options.name <<- make.names(input$options.name)
  options.data <- tryCatch(reducer(options.data,options.name,
          input$options.yn,input$options.yv,input$options.xn),
          error=function(e) NULL)
  if(input$options.scalar!=1 & !is.na(input$options.scalar)) {
    options.data[,options.name] <- options.data[,options.name]*input$options.scalar
  }
  if(input$avg & !is.null(options.data)) return(avgsem(options.data))
  options.data
})

#remove filtered out colors
reduced.cols <- reactive(if(!is.null(reduced())) {
  cols()$Color[cols()$Type %in% reduced()$Type]
})
reduced.cols.cast <- reactive(if(!is.null(reduced())) {
  cols.cast()$Color[cols.cast()$Battery.ID %in% reduced()$Battery.ID]
})

wide <- reactive({
  if("Battery.ID" %in% colnames(reduced())){
    return(dcast(reduced(), Cycle~Battery.ID,mean,value.var=options.name))
  } else{
    casted <- dcast(reduced(), Cycle~Type,mean,value.var=options.name)
    casted.sem <- dcast(reduced(),Cycle~Type,mean,
                        value.var=paste0(options.name,".SEM"))
    cnames.orig <- c(colnames(casted),
                     paste0(colnames(casted.sem[2:ncol(casted)]),".SEM"))
    #this is some shiny bug
    casted <- cbind(casted,casted.sem[,2:ncol(casted)])
    colnames(casted) <- cnames.orig
    return(casted)
  }
})
```

###Filter
```{r filter}
#filter dataset for discrete variable analysis
#filter min/max determine the bounds of the sliders
filter.min <- reactive({if(is.null(imported.sorted())) return(rep(NaN,5))
  sapply(imported.sorted()[stdnames],min)
})
filter.max <- reactive({if(is.null(imported.sorted())) return(rep(NaN,5))
  sapply(imported.sorted()[stdnames],max)
})
output$filter.voltage <- renderUI({ 
  sliderInput("filter.voltage","Select a voltage range:",filter.min()[1],filter.max()[1],
            c(filter.min()[1],filter.max()[1]),0.1)
  })
output$filter.current <- renderUI({ 
  sliderInput("filter.current","Select a current range:",filter.min()[2],filter.max()[2],
            c(filter.min()[2],filter.max()[2]),0.1)
  })
output$filter.amphours <- renderUI({ 
  sliderInput("filter.amphours","Select a capacity range:",filter.min()[3],filter.max()[3],
            c(filter.min()[3],filter.max()[3]),0.1)
  })
output$filter.totaltime <- renderUI({ 
  sliderInput("filter.totaltime","Select a total time range:",filter.min()[4],filter.max()[4],
            c(filter.min()[4],filter.max()[4]),1)
  })
output$filter.steptime <- renderUI({ 
  sliderInput("filter.steptime","Select a step time range:",filter.min()[5],filter.max()[5],
            c(filter.min()[5],filter.max()[5]),1)
  })
output$filter.step <- renderUI({ 
  sliderInput("filter.step","Is there a step to isolate? (0 for no)",0,
            tryCatch(max(imported.sorted()$Step[imported.sorted()$Step<=ceiling(quantile(
              imported.sorted()$Step,.99))]),error=function(e) 1),0,1)
})
output$filter.cycle <- renderUI({ 
  sliderInput("filter.cycle","Is there a cycle to isolate? (0 for no)",0,
              tryCatch(max(imported.sorted()$Cycle),
                       error=function(e) 1),0,1,T)
})

fluidPage(column(12,div(
  style = "height:80px;",
  htmlOutput("filter.voltage"),
  htmlOutput("filter.current"),
  htmlOutput("filter.amphours"),
  htmlOutput("filter.totaltime"),
  htmlOutput("filter.steptime"),
  htmlOutput("filter.step"),
  htmlOutput("filter.cycle")
)))

#will perform calculations on this filtered dataset
imported.filtered <- reactive(if(!is.null(imported())){
  if(is.null(input$filter.step)) return(imported())
  if(input$filter.cycle==0) x <- imported()
  else { #baseline time stamp correction
    x <- imported()[imported()$Cycle==input$filter.cycle,] %>%
    within({Total.Time <- ave(Total.Time, Battery.ID, FUN=function(x) x-min(x))}) %>%
    mutate(TimeHr=Total.Time/3600,TimeMin=Total.Time/60)
  }
  if(input$filter.step) x <- filter(x,Step==input$filter.step)
  tryCatch(filter(x,
         Voltage>=input$filter.voltage[1],Voltage<=input$filter.voltage[2],
         Current>=input$filter.current[1],Current<=input$filter.current[2],
         Amp.Hours>=input$filter.amphours[1],Amp.Hours<=input$filter.amphours[2],
         Total.Time>=input$filter.totaltime[1],Total.Time<=input$filter.totaltime[2],
         Step.Time>=input$filter.steptime[1],Step.Time<=input$filter.steptime[2]
         ),error=function(e) imported())
})
```


###Protocol
Best attempt at deriving protocol from dataset. If there is a mismatch in step numbers, you may be able to isolate what you need using the 'filter' tab.  
  
```{r protocol}
output$protocol.ids <- renderUI({ 
  selectInput("protocol.ids","Filter prediction by Battery ID:",
              c("All",levels(imported()$Battery.ID)))
  })
fluidPage(
  htmlOutput("protocol.ids"),
  renderTable(if(!is.null(imported.sorted())){
    if(input$protocol.ids=="All") Protocol(imported())
    else Protocol(filter(imported(),Battery.ID==input$protocol.ids))
  },include.rownames=F)
)
```


Column {data-width=700 .tabset .tabset-fade}
-------------------------------------

### Graph
```{r graph}
#ticker<-function(x) paste0("`",x,"`")
bar <- reactive(if(!is.null(reduced())) bargraph(reduced(),options.name,
        options.name.orig)+scale_fill_manual(values=reduced.cols(),name=""))
line <- reactive(if(!is.null(reduced())) dygraph.cast(reduced(),
        "Cycle",options.name,"Cycle",options.name.orig,
        reduced.cols.cast(),reduced.cols()))
ggline <- reactive(if(!is.null(reduced())) {
  gg <- linegraph(reduced(),"Cycle",options.name)+ylab(options.name.orig) #avg/sem
  if(input$avg) gg <- gg + scale_color_manual(values=reduced.cols(),name="") +
    scale_fill_manual(values=reduced.cols(),name="")
  else gg <- gg + scale_color_manual(values=reduced.cols.cast(),name="") #regular
  gg
})

shinyApp(
  ui = fluidPage(
    radioButtons("graphtype",NULL,c("Line"=2,"Bar"=1),inline=T),
    conditionalPanel(
        condition = "input.graphtype==1", plotlyOutput("bar")         
      ),
      conditionalPanel(
        condition = "input.graphtype==2", dygraphOutput("line"),
        tags$br(),
        textOutput("legendDivID")
      )
  ),
  server = function(input, output, session){
    output$bar <- renderPlotly(withProgress(message="Calculating...",ggplotly2(bar())))
    output$line <- renderDygraph(withProgress(message="Calculating...",line()))
  }
)
```

### Table 
```{r table}
radioButtons("tabletype",NULL,c("Long","Wide"),inline=T)
red.table <- reactive({
  if(input$tabletype=="Long") return(reduced())
  if(input$tabletype=="Wide") return(wide())
})

renderDataTable(datatable(red.table(),
  filter = 'top', rownames = F,extensions = 'Buttons',fillContainer = F,
  options = list(
    scrollX = TRUE, scrollY = TRUE, fixedColumns = TRUE,
    pageLength = 10, dom = 'Blftip',buttons = list('copy', 'csv'))),
  server=F)
```

Share {data-orientation=columns data-navmenu="Discrete"}
=====================================

Column {data-width=250 .tabset .tabset-fade}
-------------------------------------
    
### Choose options
Customize discrete variable chart for sharing:
```{r publish.options}
fluidPage(
  radioButtons("pub.type",NULL,c("Line","Bar"),inline=T),
  selectInput("pub.theme","Graph theme:",c("Default","Minimal","Grayscale")),
  selectInput("pub.legend","Legend position:",c("None","Side"="right","Above"="top",
              "Below"="bottom","Top-left"="c(0,1)","Top-right"="c(1,1)",
              "Bottom-left"="c(0,0)","Bottom-right"="c(1,0)")),
  sliderInput("pub.fsize","Font size:",10,20,12,0.5),
  textInput("pub.title","Chart title:",""),
  helpText("Download chart options:"),
  splitLayout(
    numericInput("pub.savew","Width:",12),
    numericInput("pub.saveh","Height:",8),
    downloadButton("pub.png","PNG"),
    downloadButton("pub.svg","SVG")
  )
)
#linesize?
```

###Additional Options
Customize discrete variable chart for sharing:
```{r publish.options2}
fluidPage(
  helpText("Include axis ranges:"),
  splitLayout(
    numericInput("pub.x1","X start:",NA),
    numericInput("pub.x2","X end:",NA)
  ),
  splitLayout(
    numericInput("pub.y1","Y start:",NA),
    numericInput("pub.y2","Y end:",NA)
  ),
  helpText("Horizontal line options:"),
  splitLayout(
    textInput("hline.col","Color:","None"),
    numericInput("hline.val","Position:",0),
    numericInput("hline.size","Size:",0.8,step=.2)
  ),
  checkboxInput("pub.rotatex","Rotate x-axis labels")
)
```

Column {data-width=700}
-------------------------------------

### Graph {.no-title}
```{r publish.graph}
renderPlot(withProgress(message="Rendering...",pub.graph()))
pub.graph <- reactive(if(!is.null(reduced())) {
  #these are the x-y limits
  xlim <- c(input$pub.x1,input$pub.x2)
  if(any(is.na(xlim))) xlim <- NULL
  ylim <- c(input$pub.y1,input$pub.y2)
  if(any(is.na(ylim))) ylim <- NULL
  
  if(input$pub.type=="Bar"){
    gg <- bar() + coord_cartesian(ylim=ylim)
  } 
  else { #line
    gg <- ggline() + coord_cartesian(xlim=xlim,ylim=ylim)
  }
  
  if(input$hline.col!="None" & input$hline.col!="none" & nchar(input$hline.col)){
    gg <- gg + geom_hline(aes_(yintercept=input$hline.val),linetype=2,
                          color=input$hline.col,size=input$hline.size)
  }
  if(input$pub.theme=="Default") gg <- gg + theme_gray(base_size=input$pub.fsize)
  if(input$pub.theme=="Minimal") gg <- gg + theme_bw(base_size=input$pub.fsize)
  if(input$pub.theme=="Grayscale") gg <- gg + theme_pub(base_size=input$pub.fsize) +
      scale_fill_grey(start=0,end=.9,name="") + scale_color_grey(start=0,end=.9,name="")
  
  if(!length(grep(",",input$pub.legend))) gg <- gg + theme(legend.position=input$pub.legend,
                                                           legend.title=element_blank())
  else gg <- gg + theme(legend.position=eval(parse(text=input$pub.legend)),
                        legend.justification=eval(parse(text=input$pub.legend)),
                        legend.title=element_blank())
  if(nchar(input$pub.title)) gg <- gg + ggtitle(input$pub.title)
  if(input$pub.rotatex) gg <- gg + theme(axis.text.x = element_text(angle = 60, hjust = 1))
  gg
})
output$pub.png <- downloadHandler(paste('plot-', Sys.Date(), '.png', sep=''),
   content = function(file) if(!is.null(reduced())) {
     ggsave(file,device="png",width=input$pub.savew,height=input$pub.saveh)
   }
)
output$pub.svg <- downloadHandler(paste('plot-', Sys.Date(), '.svg', sep=''),
   content = function(file) if(!is.null(reduced())) {
     ggsave(file,device="svg",width=input$pub.savew,height=input$pub.saveh)
   }
)
```
